---
title: "Forest_Plot"
author: "Mark Oremus"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
library(ggplot2)
library(ggpubr)
```

# Sex

## Create data frame with effect sizes and confidence intervals for each level of effect modification variable of interest
```{r}
a_sex<-data.frame(SEX=c(0, 1),index=1:2, Effect=c(100.47, 100.21), lower=c(100.10, 99.86), upper=c(100.84, 100.56))
```

Assumes 0 = Female and 1 = Male.

*index=1:2* because the y-axis contains two points (female and male).

## Create labels for y-axis
```{r}
sex_l<-c("Female", "Male") # Enter in the proper order: 0 = Female, 1 = Male
```

## Plot effect sizes and confidence intervals for each level, with xintercept=your unstratified beta coefficient value
```{r}
for_sex<-ggplot(data=a_sex, aes(y=index, x=Effect, xmin=lower, xmax=upper)) + geom_point() + geom_vline(xintercept=100.30, colour="blue", linetype="dashed") +geom_errorbarh(height=.1) + scale_x_continuous(name="") +scale_y_reverse(name="", breaks=1:2, labels=sex_l) + theme_classic() + ggtitle("A Path by Sex")
plot(for_sex)
```

# Age Group

## Create data frame with effect sizes and confidence intervals for each level of effect modification variable of interest
```{r}
a_age<-data.frame(AGE=c(0, 1, 2, 3),index=1:4, Effect=c(79, 90, 94, 96), lower=c(49.6, 60.6, 64.6, 66.6), upper=c(108.4, 119.4, 123.4, 125.4))
```

Assumes 0 = 45-54, 1 = 55-64, 2 = 65-74, 3 = 75+.

*index=1:4* because the y-axis contains four points (one point for each of four age groups).

## Create labels for y-axis
```{r}
age_l<-c("45-54 years", "55-64 years", "65-74 years", "75+ years") # Enter in the proper order: 0 = Female, 1 = Male
```

## Plot effect sizes and confidence intervals for each level, with xintercept=your unstratified beta coefficient value
```{r}
for_age<-ggplot(data=a_age, aes(y=index, x=Effect, xmin=lower, xmax=upper)) + geom_point() + geom_vline(xintercept=82.7, colour="blue", linetype="dashed") +geom_errorbarh(height=.1) + scale_x_continuous(name="") +scale_y_reverse(name="", breaks=1:4, labels=age_l) + theme_classic() + ggtitle("A Path by Age Group")
plot(for_age)
```

# Combine the plots

```{r}
ggarrange(for_sex, for_age, labels = c("A", "B"), nrow=1, ncol=2)
```

The combined plot can be re-sized and exported as a .png file using the *ggexport* function.